### 2020-02-09 submission/appendix.tex
clean up for submission

\begin{table}[t]
\small
\begin{center}
\begin{tabular}{|p{1in}|c|}
\hline
Figure & Jupyter Notebook \\
\hline
1  &  WeightWatcher-VGG.ipynb \\
2(a)  &  WeightWatcher-ResNet.ipynb \\
2(b)  &  WeightWatcher-ResNet-1K.ipynb \\
3(a)  &  WeightWatcher-VGG.ipynb \\
3(b)  &  WeightWatcher-ResNet.ipynb \\
3(c)  &  WeightWatcher-DenseNet.ipynb \\
\hline
5 & WeightWatcher-OpenAI-GPT2.ipynb \\
6, 7 & WeightWatcher-OpenAI-GPT2.ipynb \\
\hline
\end{tabular}
\end{center}
\caption{Jupyter notebooks used to reproduce Tables 1 and 2, and Figures 1,2,3,5,6, and 7.}
\label{table:notebooks}
\end{table}

\subsection{Reproducing Section 3, Distiller Model}

\subsection{Reproducing Table 3, Section 6}

We provide several Google Colab notebooks which can be used to reproduce the result in Table 3.
The ImageNet-1K and other pretrained models are taken from the pytorch models in the \texttt{omsr/imgclsmob} 
``Sandbox for training convolutional networks for computer vision'' github repository.
\footnote{\url{https://github.com/osmr/imgclsmob}}
The data can be generated in parallel by running each Colab notebook simultaneously on the same account,
The final results are generated with \charles{move notebooks to repo and finish}

@@

To generate the results in Table 3, we run linear for each architecture series in Table~\ref{table:architectures},
regressing each empirical log norm metric against the reported Top 1 (and Top 5) errors (as listed on the \texttt{osmr/imgclsmob} github 
repository README file. 
We filter out regressions with less than five datapoints.
We record the R-squared and mean squared errors (MSE). 
The final results for all models is provided in the \texttt{XXXXXX}.

>>>>

\begin{table}[t]
\small
\begin{center}
\begin{tabular}{|p{1in}|c|}
\hline
Figure & Jupyter Notebook \\
\hline
1  &  WeightWatcher-VGG.ipynb \\
2(a)  &  WeightWatcher-ResNet.ipynb \\
2(b)  &  WeightWatcher-ResNet-1K.ipynb \\
3(a)  &  WeightWatcher-VGG.ipynb \\
3(b)  &  WeightWatcher-ResNet.ipynb \\
3(c)  &  WeightWatcher-DenseNet.ipynb \\
\hline
4 & WeightWatcher-Intel-Distiller-ResNet20.ipynb \\
\hline
5 & WeightWatcher-OpenAI-GPT.ipynb \\
6, 7 & WeightWatcher-OpenAI-GPT2.ipynb \\
\hline
\end{tabular}
\end{center}
\caption{Jupyter notebooks used to reproduce all results in sections ~\ref{sxn:cv} and ~\ref{sxn:nlp}}
\label{table:notebooks}
\end{table}

\subsection{Reproducing Figure~\ref{fig:resnet204D5L}, Distiller Model}

We provide the orginal Jupyter Notebooks, which uses the Intel \texttt{distiller} framework
.\footnote{\url{https://nervanasystems.github.io/distiller}} in the \texttt{distiller} folder of our 
github repo. Figure ~\ref{fig:resnet204D5L} is from the  \texttt{``...-Distiller-ResNet20.ipynb''} 
notebook (see Table~\ref{table:notebooks}).  
For completeness, we provide both the results described here, and additional results
on other pretrained and distilled models using the \texttt{weightwatcher} tool.

\subsection{Reproducing Table 3, Section~\ref{xsn:all}}

We provide several Google Colab notebooks which can be used to reproduce the results in Table 3,
in the \texttt{ww-colab} folder in our github repo.  
The ImageNet-1K and other pretrained models are taken from the pytorch models in the \texttt{omsr/imgclsmob} 
``Sandbox for training convolutional networks for computer vision'' github repository
.\footnote{\url{https://github.com/osmr/imgclsmob}}
The data can be generated in parallel by running each Google Colab notebook (i.e. \texttt{ww\_kdd2020\_0\_100.ipynb}) 
simultaneously on the same account.
The final results are generated with the \texttt{ww\_kdd2020\_results.ipynb} notebook.

@@

To generate the results in Table 3, we run linear for each architecture series in Table~\ref{table:architectures},
regressing each empirical log norm metric against the reported Top 1 (and Top 5) errors (as listed on the \texttt{osmr/imgclsmob} github 
repository README file, with the relevant data extracted and provided in our github repo as \texttt{pytorchcv.html}
We filter out regressions with less than five datapoints.
We record the R-squared and mean squared errors (MSE). 
The final results for all series regressions are provided in the \texttt{ww-colab/df\_all.xslx} python pandas dataframe file.

### 2020-02-09 submission/introduction.tex
clean up for submission

The \emph{quality metrics} we consider are based on the spectral properties of the layer weight matrics.
They are based on norms of weight matrices (such norms have been used in traditional statistical learning theory to bound capacity and construct regularizers) and/or parameters of power law (PL) fits of the eigenvalues of weight matrices (such PL fits are based on statistical mechanics approaches to DNNs).
Note that, while we use traditional norm-based and PL-based metrics, our goals are different.
Unlike more common ML approaches, \emph{we do not seek a bound on the generalization} (e.g., by evaluating training/test error during training), \emph{we do not seek a new regularizer}, and \emph{we do not aim to evaluate a single model} (e.g., hyperparmeter optimization).% 
\footnote{One could of course use these techniques to improve training, and we have been asked about that, but we are not interested in that here. Our main goal here is to use these techniques to evaluate properties of state-of-the-art pretrained DNN models.}
Instead, we want to examine different models across common architecture series, and we want to compare models between different architectures themselves, and in both cases \emph{we aim to predict trends in the quality of pre-trained models without access to training or testing data}.

In more detail, our main contributions are the following.
\begin{itemize}[leftmargin=*]
\item 
%First, 
Motivated by practical problems, we formulate the question ``Can one predict trends in the quality of state-of-the-art neural networks without access to training or testing data?''
\item
%Second, 
%To answer this question, we analyze hundreds of publicly-available pretrained models, including older and current state-of-the-art models in CV and NLP.
To answer this question, we analyze hundreds of publicly-available pretrained state-of-the-art models from CV and NLP.
\item 
%Third, 
We find that norm-based metrics do a reasonably good job at predicting quality trends in well-trained models, i.e., they can be used to discriminate between ``good-better-best'' models, but they can qualitatively fail for models that may not be well-trained, i.e., to distinguish ``good-versus-bad'' models.
\item 
%Fourth, 
We find that PL-based metrics do much better---quantitatively better at discriminating good-better-best, and qualitatively better at discriminating good-versus-bad models.
\item 
%Finally, 
We find that PL-based metrics can also be used to characterize fine-scale model properties, including layer-wise \emph{correlation flow}, and evaluating post-training modifications such as model distillation, increasing the dataset size, and other model improvements.
\end{itemize}

@@

All of our computations were performed with the publicly-available \emph{WeightWatcher} tool (version 0.2.7)~\cite{weightwatcher_package};
and, in order to make our results fully reproducible, we provide Jupyter notebooks in the github repo for this paper~\cite{repo},
and with fully reproducible Google colab notebooks for the larger calculations.%
\footnote{\url{https://github.com/CalculatedContent/kdd2020} \michael{different name?}\charles{suggestions?}\michael{Anonymous, just for anonymized submission.}}
\michael{FIX THIS LINK TO: Google Colab OR THE REPO.}

>>>>

The \emph{quality metrics} we consider are based on the spectral properties of the layer weight matrics.
They are based on norms of weight matrices (such norms have been used in traditional statistical learning theory to bound capacity and construct regularizers) and/or parameters of power law (PL) fits of the eigenvalues of weight matrices (such PL fits are based on statistical mechanics approaches to DNNs).
Note that, while we use traditional norm-based and PL-based metrics, our goals are different.
Unlike more common ML approaches, \emph{we do not seek a bound on the generalization} (e.g., by evaluating training/test error during training), \emph{we do not seek a new regularizer}, and \emph{we do not aim to evaluate a single model} (e.g., hyperparmeter optimization).% 
\footnote{One could of course use these techniques to improve training, and we have been asked about that, but we are not interested in that here. Our main goal here is to use these techniques to evaluate properties of state-of-the-art pretrained DNN models.}
Instead, we want to examine different models across common architecture series, and we want to compare models between different architectures themselves, and in both cases, we ask

\emph{Can we predict trends in the quality of pre-trained models without access to training or testing data ?}.

%\begin{itemize}[leftmargin=*]
%\item 
%First, 
%Motivated by practical problems, we formulate the question ``Can one predict trends in the quality of state-of-the-art neural networks without access to training or testing data''
%\item
%Second, 
%To answer this question, we analyze hundreds of publicly-available pretrained models, including older and current state-of-the-art models in CV and NLP.
To answer this, we analyze hundreds of publicly-available pretrained state-of-the-art CV and NLP models. And we find that:
%\end{itemize}
%Third, 
%\paragraph{Our main contributions are:}
\begin{itemize}
\item
Norm-based metrics do a reasonably good job at predicting quality trends in well-trained models, i.e., they can be used to discriminate between ``good-better-best'' models, but they can qualitatively fail for models that may not be well-trained, i.e., to distinguish ``good-versus-bad'' models.
\item 
%Fourth, 
Power Law (PL)-based metrics do much better---quantitatively better at discriminating good-better-best, and qualitatively better at discriminating good-versus-bad models.
\item 
%Finally, 
PL-based metrics can also be used to characterize fine-scale model properties, including layer-wise \emph{correlation flow}, and evaluating post-training modifications such as model distillation, increasing the dataset size, and other model improvements.
\end{itemize}

@@

All of our computations were performed with the publicly-available \emph{WeightWatcher} tool (version 0.2.7)~\cite{weightwatcher_package};
and, to be fully reproducible, we only examine publically available, pretrained models, and
also provide all Jupyter and Google Colab notebooks used accompanying github 
repository\footnote{\url{https://github.com/CalculatedContent/kdd2020}
\michael{To be anonymized}}
See the Appendix for more details on how to reproduce all results.
